formula1

### 2020-06-01 inst/f1points.Rmd
use ordertable2points() instead

```{r,label=likevspoints,cache=TRUE,echo=FALSE}
jj <- read.table("formula1_2017.txt",header=TRUE)
points <- jj[,21]
names(points) <- rownames(jj)

mL2017 <- maxp(H)
m <- mL2017   # maxp(H)
ox <- round(rank(-points[seq_len(top)]))  # negative because number 1 = largest number of points
oy <- rank(-m)                            # negative because number 1 = largest strength
par(pty='s')        # square plot
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="official order",ylab="my order",main='Formula 1, 2017 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray') }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

From the above, we see that

>>>>

```{r,label=calcpoints}
p <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
dp <- ordertable2points(as.ordertable(F1_table_2017[seq_len(top),]),p)
dp <- dp[order(-dp)]
dp[] <- seq_along(dp)
dp
```
nw:

```{r,label=likevspoints,cache=TRUE,echo=FALSE}

m <- maxp(H)  # just 'top' players
ox <- dp
oy <- rank(-m)                           # minus as number 1 = largest strength
par(pty='s')        # square plot
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="official order",ylab="my order",main='Formula 1, 2017 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray') }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

From the above, we see that the first three drivers (Hamilton, Vettel,
Bottas) are respectively first, second and third according to both
ranking procedures.
